\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.3in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}
\begin{document}
\begin{center}
	{\LARGE \textbf{Raj Reddy}}\\
	\vspace{0.05cm}
	\raisebox{-0.2\height} \ \  (352) 530-3397
    \hfill\raisebox{-0.2\height} \ \ rajreddy23@outlook.com
    \hfill \raisebox{-0.2\height}  \ \ github.com/rjrddy
    \hfill \raisebox{-0.2\height}  \ \ linkedin.com/in/raj-reddy-1
     \hfill \raisebox{-0.2\height}  \ \ raj-reddy.com
\end{center}
\hrule
\vspace{-1em}
\subsection*{\Large Education}
\renewcommand\labelitemi{}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
	\item
	      \headerrow
	      {\textbf{University of Utah}}
	      {\textbf{Salt Lake City, UT}}
	      \headerrow
	      {\emph{B.S. Computer Science}}
	      {\emph{August 2020 -- May 2025}}
	      \item \textbf{Relevant Coursework:} Computer Systems, Machine Learning, Computer Graphics, Algorithms, Software Practice I \& II, Database Systems, Computer Networks, Foundations of Data Analysis, Models of Computation, and Linear Algebra.
\end{itemize}
\hrule
\vspace{-1em}
\subsection*{\Large Skills}
\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em]
    \parskip=0.1em
	\item \textbf{Languages:}
	      Python, Java, C++, C\#, SQL
	\item \textbf{Software:}
        PyTorch, Pandas, NumPy, React, Node.js, AWS, Azure, Docker, Git, REST, Django, MongoDB, Linux
\end{itemize}
\hrule
\vspace{-1em}
\subsection*{\Large Experience}
\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
        \item
	      \headerrow
	      {\textbf{L3Harris Technologies}}
	      {\textbf{Greenville, TX}}
	      \headerrow
	      {\emph{Associate Software Engineer}}
	      {\emph{June 2025 -- Present}}
	      \begin{itemize*}
                \item Developed signal processing modules in Python and C++ on embedded systems, collaborating with hardware teams to optimize performance and resource utilization.
                \item Built microservices for high-frequency data ingestion, processing, and storage, leveraging Podman and serverless functions.
                \item Automated CI/CD testing with pipelines, integrating static code analysis, and integration testing.
            \end{itemize*}
        \item
	      \headerrow
	      {\textbf{Doxy.me}}
	      {\textbf{Charleston, SC}}
	      \headerrow
	      {\emph{Software Engineering Intern}}
	      {\emph{August 2024 -- May 2025}}
	      \begin{itemize*}
                \item Built transformer-based models with PyTorch and Llama, integrating WebRTC for real-time video streaming.
                \item Deployed inference pipelines on SageMaker \& Fargate, improving diagnostic accuracy with reinforcement learning.
                \item Authored and maintained YAML-based configuration files for CI/CD pipelines, cloud infrastructure, and application deployments, enabling reproducible environments and streamlined releases.
            \end{itemize*}
    \headerrow
	      {\textbf{University of Utah}}
	      {\textbf{Salt Lake City, UT}}
	      \headerrow
	      {\emph{Undergraduate Research Assistant - FuTURES Lab}}
	      {\emph{May 2024 --  Jun 2025}}
	      \begin{itemize*}
	      	\item Analyzed and optimized large-scale datasets, enhancing software configuration testing with tools like gcov and CMake, increasing code coverage by 30\% on real-world APIs such as Libpng and PyTorch.
	      	\item Expanded OSS-Fuzz testing coverage, using compile-time options to improve the robustness of full-stack libraries.
	      \end{itemize*}
	\item
	      \headerrow
	      {\textbf{HEXstream}}
	      {\textbf{Chicago, IL}}
	      \headerrow
	      {\emph{Software Engineering Intern}}
	      {\emph{May 2022 -- Aug 2022}}
	      \begin{itemize*}
	      	\item Engineered backend ETL pipelines integrating data from 25+ enterprise sources into Azure SQL and Azure Data Lake.
            \item Developed automated workflows for ingestion, cleansing, and aggregation, supporting distributed analytics systems.
	      \end{itemize*}
\end{itemize}
\hrule
\vspace{-1em}
\subsection*{\Large Projects}
\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
    \item \textbf{University Course Planning/Review Platform:} Built a multi-service data platform enabling student schedule matching, course overlap detection, and behavioral insights. Developed ETL pipelines in Python to process thousands of course records, user preferences, and time-series activity logs. Built a responsive frontend using React + Tailwind, including interactive dashboards, heatmaps, calendar visualizations, and search interfaces.
    \item \textbf{Configuration Fuzzer:} Developed a configuration fuzzing tool for OSS-Fuzz, automating build generation to identify critical compile-time configurations and improve code coverage.
    \item \textbf{Ray Tracing Engine:} Created an interactive WebGL-based ray tracing engine in JavaScript, featuring realistic reflections, dynamic lighting, and customizable environment maps. Implemented shaders and user controls for rendering techniques, scene adjustments, and interactivity.
\end{itemize}
\end{document}
